%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}

\name{John Dengis} % Your name
\address{400 Beale St Apt 1203 \\ San Francisco, CA 94105} % Your address
% \address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(415)~$\cdot$~231~$\cdot$~8227 \\ \href{mailto:john@deng.is}{john@deng.is} \\ \href{https://www.linkedin.com/in/john-dengis/}{linkedin.com/in/john-dengis} \\ \href{https://github.com/jadengis}{github.com/jadengis}} % Phone, email, links

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY OF QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary of Qualifications}

\begin{rSubsection}{}{}{}{}
\item Engineering leader with a decade of experience scaling teams and platforms to billions in GTV.
\item Deep technical fluency across languages, platforms, distributed systems, and multi-agent systems.
\item Founder-mode operator shipping AI-native products end-to-end, architecture through delivery.
\item Skilled people manager with deep experience hiring, developing, and promoting engineers at every level.
\item Proven cross-functional partner across product, business, and external technical stakeholders.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{M.Sc in Mathematics} \hfill {September 2014 -- August 2015} \\ 
University of Toronto  \hfill {\textit{Toronto, ON}} \\
Dissertation: Special Methods for Elliptic Problems with Annular Data \\
(Average Grade: A\verb!+!)

\textbf{B.Sc in Mathematical Physics (Minor in Pure Mathematics)} \hfill {September 2009 -- June 2014} \\ 
University of Waterloo \hfill {\textit{Waterloo, ON}} \\
(Average Grade: 93.5\%)

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Underflow}{December 2025 -- Present}{Co-Founder \& CTO}{San Francisco, CA}
\item Founded AI-native company automating email-driven workflows for the insurance industry.
\item Built multi-agent systems with shared context across inbox and application.
\item Earned a California insurance broker license to ground product decisions in domain expertise.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{April 2025 -- December 2025}{Senior Engineering Manager}{San Francisco, CA}
\item Led 20 mobile and backend engineers in Fulfillment, unlocking \$300M+ in incremental GTV.
\item Owned partner relationships across retailer and third-party tech teams to build strong integrations.
\item Interviewed 100+ engineers and managers and closed multiple senior hires as a recruiting partner.
\item Drove team-wide adoption of AI coding tools, raising developer throughput and codifying best practices.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{July 2021 -- April 2025}{Engineering Manager}{San Francisco, CA}
\item Led 6 engineers improving Connect API Platform DX, launching 6 new partner integrations.
\item Established sprint, stand-up, and retro cadences that lifted team predictability and engagement.
\item Revamped engineering interview process, standardizing rubrics and improving signal quality.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{April 2020 -- July 2021}{Senior Software Engineer}{Toronto, ON}
\item Designed and implemented the v2 Fulfillment APIs, scaling order throughput to 20M+ orders.
\item Designed and shipped the modular Connect order status page, reducing bad-order rate by 40\%.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{July 2019 -- April 2020}{Software Engineer II}{Toronto, ON}
\item Founding engineer on Connect API; defined initial architecture and scaled to \$3B+ in GTV.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Coral Health Research and Discovery Inc.}{July 2018 -- April 2019}{Senior Software Developer}{Toronto, ON}
\item Designed and built the Coral Health Records application from the ground up.
\item Architected serverless infrastructure end-to-end, integrating with 200+ health systems.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Vena Solutions}{October 2016 -- July 2018}{Senior Software Developer}{Toronto, ON}
\item Reduced server boot time by 60\% via JVM and dependency-loading optimizations.
\item Improved Excel Add-in start time by 4x for enterprise users.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{October 2015 -- October 2016}{Math Library and Compiler Developer}{Toronto, ON}
\item Designed, built, and tuned a high-performance replacement for the IBM java.lang.Math library.
\item Implemented optimizations for new hardware instructions in the IBM XL Compiler.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\begin{rSubsection}{Modeling of CO2 injection into aquifers containing dissolved H2S}{May 2016}{Journal of Natural Gas Science and Engineering}{}
\item \href{https://doi.org/10.1016/j.jngse.2016.05.022}{https://doi.org/10.1016/j.jngse.2016.05.022}
\end{rSubsection}

\begin{rSubsection}{An optimal dissipative encoder for the toric code}{January 2014}{New Journal of Physics}{}
\item \href{https://iopscience.iop.org/article/10.1088/1367-2630/16/1/013023}{https://iopscience.iop.org/article/10.1088/1367-2630/16/1/013023}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\textbf{Languages}: JavaScript / TypeScript, Java / Kotlin, Go, Elixir, Ruby \\
\textbf{Platforms}: AWS, GCP, Fly.io, Postgres, Redis, Rails, Spring, React, Node.js \\
\textbf{AI / ML}: Anthropic / OpenAI SDKs, LangChain / LangGraph, Langfuse, pgvector

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
