%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\name{John Dengis} % Your name
\address{400 Beale St Apt 1203 \\ San Francisco, CA 94105} % Your address
% \address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(415)~$\cdot$~231~$\cdot$~8227 \\ \href{mailto:john@deng.is}{john@deng.is}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY OF QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary of Qualifications}

\begin{rSubsection}{}{}{}{}
\item Strong technical leader with a proven track record of driving results.
\item Extensive experience supporting and up-leveling reports at all performance levels.
\item Highly effective in implementing and fine-tuning effective team processes and maintaining high-efficiency.
\item Outstanding communication and interpersonal skills.
\item Highly adaptable and able to take on new projects or roles with ease.
\item Worked extensively with cross-functional stakeholders, both internal and external.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{M.Sc in Mathematics} \hfill {September 2014 - August 2015} \\ 
University of Toronto  \hfill {\textit{Toronto, ON}} \\
Dissertation: Special Methods for Elliptic Problems with Annular Data \\
(Average Grade: A\verb!+!)

\textbf{B.Sc in Mathematical Physics (Minor in Pure Mathematics)} \hfill {September 2009 - June 2014} \\ 
University of Waterloo \hfill {\textit{Waterloo, ON}} \\
(Average Grade: 93.5\%)

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Instacart}{July 2021 - Present}{Engineering Manager}{San Francisco, CA}
\item Led a team of 10+ engineers supporting our Fulfillment-as-a-Service integrations, unlocking an additional \$200M+ in iGTV.
\item Led a team of 6 engineers improving the developer experience of partners on the Connect API Platform.
\item Implemented effective team processes (sprints, stand-ups, retros) to keep team engaged and efficient.
\item Helped improve our engineering interview process to better vet candidates.
\item Participated extensively in the recruitement process, onboarding 3 engineers personally.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{April 2020 - July 2021}{Senior Software Engineer}{Toronto, ON}
\item Designed and implemented the v2 Fulfillment APIs and worked with partners to scale to millions of orders.
\item Designed and implemented the modular Connect order status page and reduced bad order rate by 40\%.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Instacart}{July 2019 - April 2020}{Software Engineer II}{Toronto, ON}
\item Founding member of the Connect API team.
\item Helped scale the API product to over \$3B in GTV.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Coral Health Research and Discovery Inc.}{July 2018 - April 2019}{Senior Software Developer}{Toronto, ON}
\item Designed and built from the ground-up the Coral Health Records application.
\item Designed and implemented the serverless architecture used to support the application.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Vena Solutions}{October 2016 - July 2018}{Senior Software Developer}{Toronto, ON}
\item Designed and implemented new back-end APIs to satisfy evolving customer needs.
\item Delivered mission critical performance enhancements across the entire software stack.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{October 2015 - October 2016}{Math Library and Compiler Developer}{Toronto, ON}
\item Designed, built and tuned a high performance replacement for the current IBM java.lang.Math library.
\item Implemented exploitations and optimizations for new hardware instructions in the IBM XL Compiler.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\begin{rSubsection}{Modeling of CO2 injection into aquifers containing dissolved H2S}{May 7, 2016}{Journal of Natural Gas Science and Engineering}{}
\item \href{https://doi.org/10.1016/j.jngse.2016.05.022}{https://doi.org/10.1016/j.jngse.2016.05.022}
\end{rSubsection}

\begin{rSubsection}{An optimal dissipative encoder for the toric code}{January 16, 2014}{New Journal of Physics}{}
\item \href{https://iopscience.iop.org/article/10.1088/1367-2630/16/1/013023}{https://iopscience.iop.org/article/10.1088/1367-2630/16/1/013023}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
